---
title: "sta_100_hw_1"
author: "Tiffany Chan"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



```{r}
pain<-read.csv("data/pain.csv")
```



#(a) Find the overall mean of pain tolerance, regardless of hair color.
```{r}
mean(pain$Score)
```

#(b) Find the overall standard deviation of pain tolerance, regardless of hair color.
```{r}
sd(pain$Score)
```

#(c) Find the mean pain tolerance for the category Dark-Brunette. Hint: Use R to find the mean for each group.
```{r}
aggregate(Score~HairColor,pain,mean)
```

#(d) Find the standard deviation of pain tolerance for the category LightBrunette. Hint: Use R to find the standard deviation for each group.
```{r}
aggregate(Score~HairColor,pain,sd)
```

#(e) Find the number of subjects that were in the category LightBlond. Hint: Use R to find the number of subjects for each group.
```{r}
aggregate(Score~HairColor,pain,length)
```

#(f) Which hair color category had the highest average pain tolerance?

#Light Blondes had the highest average pain tolerance.

#(g) Which hair color category had the lowest standard deviation of pain tolerance?

#Light Brunettes had the lowest standard deviation of pain tolerance.

#(h) Which hair color category had the most subjects?

#Dark Blonde,Dark Brunette, and Light Blonde tied for having most subjects

